%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Thanks : Rishi Shah 's Contribution
% inspired by his awesome contribution:
% https://www.overleaf.com/articles/rishi-shahs-resume/vgxvkmxktyxn
% Author : Allianzcortex
% contact me : github.com/Allianzcortex
% email : iamwanghz#gmail.com
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.40in,top=0.3in,right=0.75in,bottom=0.1in]{geometry} % Document margins
\usepackage{fontawesome}
\usepackage{times}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    %linkcolor=blue,
    %filecolor=magenta,      
    urlcolor=blue,
    %pdftitle={Overleaf Example},
    %pdfpagemode=FullScreen,
    }
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
% \begin{center}
% {\centerline {\em \textbf {Seeking for a fulltime internship from Sep 2019 - Apr 2010(8 months) } } }
% \end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%===========================Section 1, normal resume ===========================%

\name{Jake Underland} % Your name 


%\address{\faMapPin 204-0003 Nakazato 5-629-1, Kiyose, Tokyo} % Your secondary addess (optional)
\address{\faGithub{ github.com/jaked0626}$\:\vline\:$ \faLink \href{https://www.linkedin.com/in/jake-underland-720126201/}{LinkedIn}$\:\vline\:$ \faEnvelope{ jakez0626@gmail.com}}
\address{\faMapMarker{ 5-629-1 Nakazato, Kiyose, Tokyo, JPN 204-0003 }$\vline$ \faPhone (+81)90 1461 8440} % Your address

\begin{document}
{\centerline {\em \textbf { Looking for full-time and internship opportunities in data science, software engineering, and related fields. } } }
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Chicago (GPA 3.93/4) } \hfill {\em September 2020 - July 2021} 
\\- International Student-at-Large
%\\- Studied STEM subjects with a focus on furthering statistical literacy and gaining hard skills such as programming and data analysis methods.
\\- Led research team of undergraduates analyzing the efficacy of educational policies in the US. 
\\- Relevant Courses: Abstract Linear Algebra, Statistical Theory and Methods I \& II (Frequentist and Bayesian inference, regression theory), Micro and Macro (Neoclassical growth model), Econometrics, Computer Science with Applications \href{https://www.classes.cs.uchicago.edu/archive/2020/fall/12100-1/}{I}, \href{https://www.classes.cs.uchicago.edu/archive/2020/winter/12200-1/}{II} \& \href{https://www.classes.cs.uchicago.edu/archive/2021/spring/12300-1/}{III}.

{\bf Waseda University - School of Political Science and Economics (GPA 3.7/4) } \hfill {\em April 2019 - March 2023} 
\\- \href{http://www2.cie-waseda.jp/glfp/jp/about/program.html}{Global Leadership Fellows' Program} fellow
\\- Conducting research under \href{https://tadaohoshino.wordpress.com/}{Professor Hoshino} on applications of machine learning in economics, under \href{https://waseda.pure.elsevier.com/en/persons/hisatoshi-tanaka}{Professor Tanaka} on statistical and econometric theory. 
\\- Relevant courses: Mathematical Analysis, Game Theory, Dynamic Models (Macro), Optimization, Algorithms, Public Economics. 

%
%{\bf Tosei Gakuen High School (GPA 4/4) } \hfill {\em April 2016 - March 2019} 
%\\- President of Student Council: Installed gender neutral school uniform.


\end{rSection}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Professional Experience}

{\bf CreateBase }[\href{https://createbase.work/}{link}] \hfill {\em Jun 2021 - Present} \\
{\textit{Full stack Developer Intern }}
\\- Developed web application \textit{Chinascope} in PHP+Laravel framework. 
\\- Developed logging infrastructure for unmanned workstations, incorporated image recognition to improve accuracy of logging system. 

{\bf Bank of Japan} \hfill {\em Sep 2021 - Oct 2021} \\
{\textit{IT Department 2-Day Summer Internship}}
\\- Participated in workshop debating the installment of a Central Bank Digital Currency (CBDC) in Japan.

{\bf Morgan Stanley} \hfill {\em Aug 2021} \\
{\textit{IT + Firmwide Summer Insights Programs}}

{\bf CATAL English School }[\href{https://catal.jp/}{link}] \hfill {\em 2020 - Present}

{\bf Private Tutor/Translator} \hfill {\em 2019 - Present} 

\end{rSection}

%----------------------------------------------------------------------------------------
%	COMMUNITY INVOLVEMENT
%----------------------------------------------------------------------------------------
\begin{rSection}{Extra Curricular}

{\bf Google Developer Students Club }[\href{https://gdsc.community.dev/waseda-university/}{link}] \hfill {\em September 2021 - Present} \\
{\textit{Backend Lead}}\\
- Leading a team of 20+ engineers
\\- Improved coding efficiency by creating specializations within Backend Team and distributing code reviews based on specializations.

%{\bf Hospital Volunteer} \hfill {\em 2016 - 2019} \\
%{\textit{Translator}}

{\bf Catholic Commission of Japan for Migrants, Refugees and People on the
Move} [\href{https://www.cbcj.catholic.jp/english/japan/comt/migrantsrefugees_e/}{link}] \hfill {\em 2015 - Present} \\
{\textit{Caretaker, Educator, Translator}}

{\bf Himawari Children's Group } [\href{https://www.waseda.jp/inst/wavoc/news/2020/04/01/5313/}{link}] \hfill {\em 2019 - 2020} \\
{\textit{Caretaker for children with special needs}}

\end{rSection}

%----------------------------------------------------------------------------------------
%       CERTIFICATES
%----------------------------------------------------------------------------------------

\begin{rSection}{Certificates}
- Japan Statistical Society Certificate Level 3, Best Grade, 2019 \\
- Waseda University Arai Takanobu Scholarship
\end{rSection}

%===========================Section 2, technical resume ===========================%
\newpage

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages: \ & Japanese (Native), English (Native) \\
Computer Languages: \ & Python, PHP, R, C, SQL \\
Software \& Tools: & {\textbf{Backend: }}Python+Django, PHP+Laravel\\
& {\textbf{Data Science: }}R+Rstudio, Pandas, NumPy, Matplotlib, Scikit-learn. \\
& {\textbf{Others: }} Docker, Heroku
\end{tabular}

\end{rSection}

% \begin{rSection}{Carrier Objective}
%  To work for an organization which provides me the opportunity to improve my skills and knowledge to grow along with the organization objective.
% \end{rSection}
%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Projects}

{\bf Course Search Engine for University of Chicago}
\\- Linked \href{https://github.com/jaked0626/course_search_engine}{here}. 
\\- Crawled web for course information. 
\\- Included distance between buildings and time to travel between buildings as feature. 


{\bf Bike Share Station Prediction - Gradient Boosting}
\\- Linked \href{https://github.com/jaked0626/bikeshare-gradientboost}{here}. 
\\- Used gradient-boosting to predict number of available bikes at given bikeshare station at given time. 

{\bf Vaccine Reservation RPA}
\\-  Linked \href{https://github.com/jaked0626/Vaccine_reservation_tool}{here}. 
\\- Used Selenium to automate vaccine reservation process of Japan's Ootemachi mass vaccination center. 
\\- Helped many busy youth procure a vaccine reservation during the height of Japan's Covid-19 pandemic. 

{\bf Original Hash Table and Markov Model for Speaker Attribution}
\\- Linked \href{https://github.com/jaked0626/markov_speaker_attribution}{here}. 
\\- Designed an implementation of a hash table on Python using association lists. 
\\- Used Markov Model for speaker identification software. 

{\bf Game Theory Iterative Elimination Program}
\\- Linked \href{https://github.com/jaked0626/game_reduction}{here}. 
\\- Useful tool for reducing games by eliminating dominated strategies. Basic Game Theory. 

{\bf Educational Policy Analysis Software}
\\- Linked \href{https://github.com/jaked0626/EduPRJ}{here}. 
\\- Crawled web for US educational policy software 

{\bf MapReduce for Whitehouse}
\\- Linked \href{https://github.com/jaked0626/mrjob}{here}. 
\\- Used mrjob to employ MapReduce for large data analysis.

{\bf Econometrics Coursework}
\\- Linked \href{https://github.com/jaked0626/ECONOMETRICS-ECON21020}{here}. 
\\- Proofs. 

{\bf Policy Analysis Coursework}
\\- \href{https://github.com/jaked0626/soc-safety-net-empirics/blob/main/Pset3/annotated-Pset3.pdf}{Differences-in-Differences} and  \href{https://github.com/jaked0626/soc-safety-net-empirics/blob/main/Pset4/Pset4.pdf}{IV estimation of LATE}. 

{\bf Real Analysis Coursework}
\\- Linked \href{https://github.com/jaked0626/some-proofs}{here}. 
\\- Proofs. 



\end{rSection}

%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

% \begin{rSection}{Academic Achievements} 
%  Runners up in B.G.Shirke Vidyarthi Competition for Innovative Project organized by Pune Construction Engineering Research Foundation in January 2018
% \item Won First Prize in Model Making Competition Organized by Symbiosis Institute of Technology, Pune.
% \end{rSection}

% \newpage

%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------
% \begin{rSection}{Extra-Cirrucular} \itemsep -3pt
% \item Co-Organized “ Nirmitee 2017” - a National Symposium of Civil Department of MIT, Pune
% \item Attended a workshop on Autodesk Revit at IIT Bombay in 2014.
% \item Winner of Inter Departmental Football Competition 2015.
% \item Member of the  Rotaract Club Of Pune Pride from 2014 to 2017.
% \item Worked for a start-up company Named OUST as a Regional Marketing Manager
% %\item Trained and disciplined in National Cadet Corps (NCC), IIT Kanpur for a year.
%  %\item  Participated in Vijyoshi Camp 2012 organized at Indian Institute of Science, Bangalore.
%  %\item Won 2nd position in Kho-Kho in Intramurals conducted by Physical Education Section, IIT Kanpur.
%  %\item Pursued French as second language during secondary school from Grade 6 to Grade 10. Also participated in French Song Competition and French G.K. Quiz in Class 10th. %

% \end{rSection}

% \begin{rSection}{Personal Traits}
% \item Highly motivated and eager to learn new things.
% \item Strong motivational and leadership skills.
% \item Ability to work as an individual as well as in group.
% \end{rSection}
\end{document}
